Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-16 paper/structureScene.tex
Edit results section
I changed the order, per the ordering of the rest of the paper. I
also removed the log-compression part of the ASSR experiment. The
advantage of the log is already in a sense established by the ASC
experiments, so we can gain some space (and repeat ourselves a
little less) but removing this part. Of course, we can always put
it back in.

\begin{figure}[t]
\begin{center}
\includegraphics[width=.9\columnwidth]{bw/unsupervised_test1}
\caption{Acoustic scene similarity retrieval (ASSR) in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for scattering coefficients, with and without logarithmic compression, as a function of the rank $k$. \ja{Why not \emph{ob-a} here? Also, the relationship between the different approaches for the regular scattering coefficients seems to be inverted with respect to the log-scattering and the previous figure. That is, here we have \emph{early} $>$ \emph{ob-w} $\approx$ \emph{ob-c} instead of \emph{ob-w} $>$ \emph{ob-w} $>$ \emph{early}.}}
\label{fig:ASS_2}
\end{center}
\end{figure}

@@

\subsection{Acoustic Scene Similarity Retrieval}

This section presents evaluation results for the ASSR settings. The $p@k$ for different settings are shown in Figures \ref{fig:ASS_2} and \ref{fig:ASS_1}, illustrating the effect of the different similarity metrics and the influence of the logarithm, respectively.

@@

Outcomes for the scattering with and without logarithmic compression are shown in Figure \ref{fig:ASS_2}. It can be seen that the logarithmic compression strongly improves the results, especially for the \emph{ob} approaches, which perform worse than \emph{early} without the logarithmic compression.

@@

\subsection{Acoustic Scene Classification}

Surprisingly, although we ran a large number of experiments to formulate the relevance-based quantization scheme into a supervised setting for acoustic scene classification, none managed to outperform the baseline strategy in \emph{late} temporal integration, namely majority voting. Among such methods, the best result is achieved by the \emph{ob-c} approach with log-compressed scattering coefficients, reaching an accuracy of $66\% \pm 7$. \ja{Why don't we display these results?} \ml{I agree, we should put the results} This might be due to the fact that the discriminability gained by the relevance-based quantization approach is already achieved by the classifiers during training and the fact the relevance-based quantization approach is equivalent to an early fusion approach, which in the case of the DCASE 2013 has not been identified as beneficial due to the dataset size (see discussion in Section \ref{sec:eili}). \ja{This sentence is very confusing.}

Logarithmic compression provides a small, albeit consistent boost to acoustic scene classification over all folds in the DCASE 2013 private dataset.
Indeed, as discussed in subsection \ref{sec:logcomp}, and observed in Figure \ref{fig:compression}, the statistical assumption of normality for scattering coefficients is only approximately satisfied once mapped to a logarithmic, decibel-like scale. This transformation improves the discriminative power of the SVMs trained on scattering coefficients, regardless of the chosen temporal integration strategy (early or late) and the inner product kernel (linear or Gaussian RBF).
Again, this is in accordance with our previous findings on acoustic scene similarity retrieval, which are reported in Figure \ref{fig:ASS_2}.

>>>>

@@

The results on acoustic scene classification illustrate the superior performance of the log-scattering transform coupled with late integration, confirming the ideas motivating the construction of our cluster-based auditory scene representation. Using this representation for auditory scene similarity retrieval, we obtain results that improve significantly over traditional BOF and summary approaches, both with log-scattering features and MFCCs.

@@

Logarithmic compression provides a small, albeit consistent boost to acoustic scene classification over all folds in the DCASE 2013 private dataset.
Indeed, as discussed in subsection \ref{sec:logcomp}, and observed in Figure \ref{fig:compression}, the statistical assumption of normality for scattering coefficients is only approximately satisfied once mapped to a logarithmic, decibel-like scale. This transformation improves the discriminative power of the SVMs trained on scattering coefficients, regardless of the chosen temporal integration strategy (early or late) and the inner product kernel (linear or Gaussian RBF).

This section presents evaluation results for the ASSR settings. The $p@k$ for different settings are shown in Figure \ref{fig:ASS_1}, illustrating the effect of the different similarity metrics.

@@
